---
title: "COVID Vaccine World Map"
author: "Elena Civati"
date: "5/4/2021"
output: 
  html_document: 
    fig_width: 9.5
    fig_height: 7
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```


This interactive map shows available data at `r Sys.Date()` about COVID-19 incidence and vaccination rate across countries.  
Data are estrapolated from [Our World In Data COVID-19 Dataset](https://github.com/owid/covid-19-data). For each country, I used informations relative to the more recent date for which the total number of vaccinated people was reported, as shown in Table 1.For this reason, **the date to which data refers can be different for each country**.  
In [this GitHub repo](https://github.com/Elenena/COVIDmap) you can find the code that generates this web page, automatically working with the most up-to-date version of the dataset provided by Our World in Data (usually, it's updated on a daily basis).  
In the map, you can visualize informations as follows:  
- Clicking over a circle shows a popup with all the informations, as well as the the date to which they refers.  
- Circles are colored accordingly to the number of new cases reported for that given day.  
- The area of circles is proportional to the percentage of people that received at least one dose of COVID-19 vaccine.  
- The tickness of the border, when shown, is proportional to the percentage of people who completed the vaccination course.  

```{r}
library(CoordinateCleaner)
data("countryref")
download.file("https://covid.ourworldindata.org/data/owid-covid-data.csv", "covid.csv")
covid<-read.csv("covid.csv")
library(dplyr)
covid<-covid %>% select(location, date, new_cases_per_million, people_vaccinated_per_hundred, people_fully_vaccinated_per_hundred) %>% filter(location %in% unique(countryref$name), !is.na(people_vaccinated_per_hundred)) 

recent<-covid %>% group_by(location) %>% summarize(rownumber=which(date==max(date)), date=date[rownumber], new=round(new_cases_per_million[rownumber]/10), vacc=people_vaccinated_per_hundred[rownumber], fully=people_fully_vaccinated_per_hundred[rownumber])

covid<-select(recent, -rownumber)

library(xtable)
xt<-xtable(covid, caption = "Table 1")

countryref<-countryref %>% filter( type=="country",name %in% covid$location) %>% select(location=name, lng=centroid.lon, lat=centroid.lat)  
countryref<-group_by(countryref, location) %>% summarize(lng=mean(lng), lat=mean(lat))

data<-merge(covid, countryref)
data$popup=paste("<strong>",data$location,"</strong>", "<br>", "Date", data$date, "<br>", "Primovaccinated people:", data$vacc, "%", "<br>", "Fully vaccinated people:", data$fully, "%", "<br>", "<em>Incidence:</em>", "<em>",data$new,"</em>","<em>/100000 people/day </em>")

data$col<-ifelse(is.na(data$new),"gray",ifelse(data$new<10, "green", ifelse(data$new>25, "red", "yellow")))


library(leaflet)
map<-leaflet(data, options = leafletOptions(minZoom=1.5)) %>% addTiles() %>% addCircleMarkers(popup=data$popup, radius=sqrt(data$vacc)*4+1, weight = 1+6*data$fully/100, fillColor = data$col) %>% addLegend(colors= c("gray", "green", "yellow", "red"), labels =c("Not available", "< 10 new cases/100000 people", "from 10 to 25 new cases/100000 people", "> 25 cases/100000 people"), title="Daily incidence")


map

```

## Data

```{r results="asis"}
print(xt, type="html", caption.placement="top")

```

